A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-11-21 pilot-publication/manuscript.Rmd
Add Jin review

Despite the widespread use of these training programs there are no
controlled trials showing that they impact patient outcomes
[@Mohammad2013; @Jayaraman2014; @Kadhum2020]. But there is level 1
evidence that these programs improve provider skills and practices
[@Ali1995; @Ali1996], and observational data suggesting that
they also improve patient outcomes [@Qin2019].

>>>>

Despite the widespread use of these training programs there are no
controlled trials showing that they impact patient outcomes
[@Mohammad2013; @Jayaraman2014; @Kadhum2020]. A systematic review
report that hospital trauma training is associated with a reduction of
patient mortality with 29% (95% CI 4-47%) based on seven studies that
were either observational or uncontrolled trials [@Jin2021].
